\section{Project Description}

\subsection{What is this project? What has this project accomplished?}

Our final project is a web application which 
models a functioning job board, 
containing all the basic components
such as applicants applying to job postings, 
companies posting jobs,
scheduling interviews for applications, 
and finally decisions from both applicants and companies regarding the application. 
A job posting can either be an internship or a full time job. 
Interviews can be one of online assessment, phone screen, onsite interview, or team matching. 
We also included an information session functionality so applicants can get to know about their jobs and companies more. 

To start, the project successfully allows for 
companies to add their own postings to the website,
as demonstrated by the insertion query
screenshotted in section 6.
Additionally,
the project allows for companies to make decisions
on accepting or rejecting candidates,
with the update query.
Finally, statistics regarding the project
can also be looked up,
e.g. finding the number of recruiters per company.

\subsection{Discrepancies between final and turned in schema}

Internship and full time changed to postings.
Added interview relation in order to implement ISA relationship.
Renamed a few relations, but functionally the same.
We change the implementation of the ISA relationship for \texttt{Posting} (internship or full time). 
We implement it by adding an attribute called \texttt{PostingType} to \texttt{Posting} 
so it's easier and more efficient to get data from the 
\texttt{JobApplication} and \texttt{Posting} relationship. 
The other minor changes are name change from \texttt{Application} to 
\texttt{JobApplication}, and 
\texttt{InformationSessionHosting} to \texttt{InformationSession} for clarity purposes.
